---
title: "Lab 01 - Hello R"
author: "YG"
date: "1/23/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

```{r}
dim(datasaurus_dozen)
datasaurus_dozen$dataset<-as.factor(datasaurus_dozen$dataset)
summary(datasaurus_dozen)
table(datasaurus_dozen$dataset)
```


### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x,y))
```

### Exercise 3

Plot the star dataset.

```{r plot-star}
star_data<-datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x=x, y=y)) +
  geom_point()
```

Calculate the correlation between x and y for the star dataset.

```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.




